---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# puniform

The puniform package provides meta-analysis methods that correct for
    publication bias. Four methods are currently included in the package.
    The p-uniform method can be used for estimating the average effect size,
    testing the null hypothesis of no effect, and testing for publication bias 
    using only the statistically significant effect sizes of primary studies. The 
    second method in the package is the p-uniform* method. This method is an extension 
    of the p-uniform method that allows for estimation of the average effect size 
    and the between-study variance in a meta-analysis, and uses both the statistically 
    significant and nonsignificant effect sizes. The third method in the package 
    is the hybrid method. The hybrid method is a meta-analysis method for combining 
    an original study and replication and while taking into account statistical 
    significance of the  original study. The p-uniform and hybrid method are based 
    on the statistical theory that the distribution of p-values is uniform conditional 
    on the population effect size. The fourth method in the package is the 
    Snapshot Bayesian Hybrid Meta-Analysis Method. This method computes posterior 
    probabilities for four true effect sizes (no, small, medium, and large) based 
    on an original study and replication while taking into account publication bias 
    in the original study. The method can also be used for computing the required 
    sample size of the replication akin to power analysis in null hypothesis 
    significance testing.

## Installation

The latest release can be installed directly in R with:

```{r installation, eval = FALSE}
install.packages("puniform")
```

You can install the development version of the puniform package from GitHub with:

```{r gh-installation, eval = FALSE}
install.packages("devtools")
devtools::install_github("RobbievanAert/puniform")
```

## Additional information about the package

The puniform package was written by [Robbie C.M. van Aert](www.robbievanaert.com).
If you suspect a bug, please report a report [here](https://github.com/RobbievanAert/puniform/issues).